Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-16 paper/paper.tex
Iterate Future Work

\section{Future Work \tbr}
\label{sec:future-work}

Google plans to implement optimistic parallel reads but it turns out that
implementing this is non-trivial. They also want to support direct configuration
changes of the Paxos state machines and to reduce $\epsilon$ to be $\leq 1ms$ to
improve the performance if data is sharded between nearby datacenters.

Moreover, the node-local performance can be improved for complex queries. By now,
node-local data structures are designed for key-value accesses and these could be
improved by algorithms and data structure from database literature.

To improve the performance even further, Google plans to move processes between
datacenters if the data they operate on is moved. This would have a high impact
because the performance of the processes is close to optimal if the data is as
local as possible. However, moving processes between datacenters raises even more
complex problems.

>>>>

\section{Future Work}
\label{sec:future-work}

Google plans to implement optimistic parallel reads but it turned out that
implementing it is non-trivial. They also want to support direct configuration
changes of the Paxos state machines and to reduce $\epsilon$ to be $\leq 1ms$ in
order to improve the performance if data is sharded between nearby datacenters.

Moreover, the node-local performance could be improved for complex queries. By
now, node-local data structures are designed for key-value accesses and these data
structures could be improved by algorithms and data structure from database
literature.

To improve the performance even further, Google plans to move processes between
datacenters if the data on which they operate is moved. This would have high
impact because the performance of the processes is close to optimal if the data
is as local as possible. However, moving processes between datacenters raises
even more complex problems.
